### 2016-06-25 Chapters/paper1.tex
xxx

In this chapter we introdue a linear/nonlinear stabilized FE formulations to approximate hyperbolic problems (and by extension singular limits of CDR systems). The outcomes of this research are:
\begin{itemize}
\item  We extend the NPS technique proposed in \cite{badia_stabilized_2012} for pressure stabilization to convection stabilization. We carry out the stability and convergence analysis, getting full control on the convection term (times a stabilization parameter).\footnote{This is an improvement of our analysis with respect to the one in \cite{rebollo_high_2013} for a similar formulation, which only provides partial control over convection, i.e., the component orthogonal to the FE space with respect to the aforementioned projector. However, the analysis in \cite{rebollo_high_2013} is not restricted to quasi-uniform meshes.}
\item Next, we show how to weight this linear stabilization in such a way that it  does not affect the potential  monotonicity of the underlying method. The use of the Scott-Zhang projector in the NPS stabilization turns out to be essential to design a linear stabilization that allows one to preserve DMP properties. 
\item Then we present some nonlinear stabilization methods, i.e., shock-capturing schemes, with some  monotonicity properties. In particular, we design a method that enjoys a DMP for time-dependent multidimensional linear transport problems. 
%\item One of those methods is defined for the 1$D$ Burgers' equation and it is proved in  \cite{burman_nonlinear_2007} that it is not only monotonic but also entropy stable; thus an alternative blending between this nonlinear stabilization and the Scott-Zhang term is proposed in order to ensure that the combination mantains entropy stability.  
\item   We present a detailed numerical experimentation, where we show the excellent performance of the proposed algorithms in terms of elimination of oscillations, compared to some up-to-date shock-capturing schemes. 
%Using numerical experimentation, we show that one of the novel shock capturing techniques proposed in this work, %which can be considered a multidimensional extension of the one in \cite{burman_nonlinear_2007}, 
%produces results superior to any of the best up-to-date schemes, since it is provably monotonic. % (see \cite{john_spurious_2007,john_spurious_2008}). 
\end{itemize}

@@

Let us define $\bar{\delta} := c_{\delta} {h}{\| \beta \|_{L^\infty(\Omega)}^{-1}}$ if $\| \beta \|_{L^\infty(\Omega)}>0$ and $\bar{\delta} = 0$ otherwise. In the numerical analysis, we will assume that $\beta(t) \not = 0$ for any $t \in (0,T)$ for the sake of brevity, since the extension is obvious. Using the previous lemma we obtain the following stability result.
\begin{theorem}[Stability]
The solution $u_h$ of problem \Eq{SZstab} with the linear stabilization term $s_h(\cdot,\cdot)$ defined either by \Eq{stproj1} or \Eq{stproj2} and the projector $\kappa_h(\cdot)$ defined in \Eq{projSZ} 
%(either for the definitions \Eq{stproj1} or \Eq{stproj2} of the stabilization term) 
satisfies the bound
%$$
%\| u_h\|_{L^\infty(0,t^*;L^2(\Omega))} + \| \delta^\half \beta \cdot  \kappa_h
%^{\perp}(\nabla u_h)\|_{L^2(0,t^*;L^2(\Omega))} + \| |\beta \cdot n|^\half u_h\|_{L^2(0,t^*;L^2(\Gamma_{\rm out}))} \lesssim \|u_0\| + \|f\|_{L^\infty(0,t^*;L^2(\Omega))},
%$$
$$
\| u_h\|_{L^\infty(0,t^*;L^2(\Omega))} + \|s_h(u_h,u_h)\|_{L^2(0,t^*)} + \| |\beta \cdot n|^\half u_h\|_{L^2( \Gamma_{\rm out} \times (0,t^*))} \lesssim \|u_0\| + \|f\|_{L^1(0,t^*;L^2(\Omega))},
$$
for any $t^* \in (0,T)$. Further, it satisfies the weak inf-sup condition
\begin{align}\label{eq-dinfsup}
%\| \bar{\delta}^\half \beta \cdot \nabla u_h \| \lesssim  \| \bar\delta^\half\beta \cdot \kappa_h^{\perp}( \nabla u_h)\|  +
%\bar\delta^\half \|\beta\|_{W^{1,\infty}(\Omega)}  \|u_h\| + \sup_{\phi_h \in V_{h,0}} \frac{(\bar\delta^\half \nabla \cdot (\beta u_h),\phi_h)}{\|\phi_h\|}.
\| \bar{\delta}^\half \beta \cdot \nabla u_h \| \lesssim   s_h\left(u_h,u_h\right)  +
\gamma \bar\delta^\half \|\beta\|_{W^{1,\infty}(\Omega)}  \|u_h\| + \sup_{\phi_h \in V^k_{h,0}} \frac{(\bar\delta^\half \nabla \cdot (\beta u_h),\phi_h)}{\|\phi_h\|},
\end{align}
where $\gamma = 1$ for the stabilization term \Eq{stproj1} and $\gamma = 0$ for \Eq{stproj2}.
\end{theorem}

@@

Finally, we prove error estimates for this algorithm. We remark that linear projection stabilization methods are weakly consistent, i.e., the consistency error does not spoil the overall convergence rates, as soon as the projector $\kappa_h$ in \Eq{projSZ} has optimal approximation properties, i.e., for any $v\in W^{l,p}(\Omega)$ and $0\leq s \leq l \leq k+1$, it holds:
\begin{align}\label{eq-orthapprox}
\|\kappa_h^\perp(v)\|_{W^{s,p}(K)} \lesssim h^{l-s} \|v\|_{W^{l,p}(S_K)}, \qquad 
\|\kappa_h^\perp(v)\|_{W^{s,p}(\Omega)} \lesssim h^{l-s} \|v\|_{W^{l,p}(\Omega)},
\end{align}
where $S_K$ is a domain made of the elements neighboring $K$ (see \cite{brenner_mathematical_2010}).  We consider first the analysis for the  symmetric stabilization \Eq{stproj1}.
\begin{theorem}[Convergence]\label{th:conv}
Let $u_h \in V_h^k$ be the solution of \Eq{SZstab} with the linear stabilization term $s_h(\cdot,\cdot)$ defined in  \Eq{stproj1}  and the projector $\kappa_h(\cdot)$ defined in \Eq{projSZ}. Let us assume that the solution $u$ of \Eq{probcont} belongs to $L^\infty(0,T;H^l(\Omega))$ for $l \leq k+1$, and $\beta\in L^\infty(0,T;W^{1,\infty}(\Omega))$. The following error estimate holds for any $t^* \in (0,T)$:
\begin{align*}
& \|(u_h-u)(t^*)\| + \| \delta^\frac{1}{2} \bb \cdot \szpp \nabla  (u_h-u) \|_{L^2(\Qq)}   \\
%& \|(u_h-u)(t^*)\| + \|s_h(u_h-u,u_h-u)\|_{L^2(0,t^*)}   \\
%& \qquad \lesssim   h^{l} \|u(t^*)\|_{H^l(\Omega)}  +  h^{l-\half}\|\bb\|_{L^{\infty}(\Omega)}^\half \|u\|_{L^2(0,t^*;H^l(\Omega))} \left( 1 +  \exp\left( h t^* \|\bb\|_{W^{1,\infty}(Q)}^2\right)\right),
& \qquad \lesssim 
  h^{l} \|u(t^*)\|_{H^l(\Omega)}  +  h^{l-\half}\|\bb\|_{L^{\infty}(\Qq)}^\half \|u\|_{L^2(0,t^*;H^l(\Omega))} \left( 1 + e^{t^* {\bar \delta } \|\bb  \|^2_{L^\infty(0,t^*;W^{1,\infty}(\Omega))}}
% \exp\left( t^* \left\|{\bar \delta {\|\bb\|_{W^{1,\infty}(\Omega)}^2}}\right\|_{L^\infty(0,t^*)}\right)
\right). 
\end{align*}
\end{theorem}

@@

\begin{theorem}[Convergence]\label{th:conv2}
Let $u_h \in V_h^k$ be the solution of \Eq{SZstab} with the linear stabilization term $s_h(\cdot,\cdot)$ defined in  \Eq{stproj2} and the projector $\kappa_h(\cdot)$ defined in \Eq{projSZ}. Let us assume that the solution $u$ of \Eq{probcont} belongs to $L^\infty(0,T;H^l(\Omega))$ for $l \leq k+1$, and $\beta\in L^\infty(0,T;{H}^s(\Omega))$ for $s>\max \{ l -1, \frac{d}{2}\}$. Then, the following error estimate holds for any $t^* \in (0,T)$:
\begin{align*}
& \|(u_h-u)(t^*)\| + \| \delta^\frac{1}{2}  \szpp (\bb \cdot\nabla  (u_h-u)) \|_{L^2(\Qq)}   \cl \quad &\lesssim    h^{l} \|u(t^*)\|_{H^l(\Omega)}  +  h^{l-\half} \|\bb\|_{L^{\infty}(\Qq)}^\half \|u\|_{L^2(0,t^*;H^l(\Omega))}
+ h^{l-\half}  \| C_\beta(t) \|u\|_{H^l(\Omega)} \|_{L^2(0,t^*)},
%+ h^{l-\half} \left \| \frac{\|\bb\|_{H^s(\Omega)} }{  \|\bb\|^\half_{L^\infty(\Omega)}} \|u\|_{H^l(\Omega)} \right \|_{L^2(0,t^*)}.
%, %\qquad \hbox{for any $t^* \in (0,T)$.}
\end{align*}
where $C_\beta=\min_{K \in \mathcal{T}_h} \|\beta\|_{H^{l-1}(S_K)}\|\beta\|^{-\half}_{L^\infty(K)}$.
\end{theorem}
\begin{proof}
The proof is similar to the one for Theorem \ref{th:conv}. Due to \cite[Th. $1.4.4.2$]{grisvard2011elliptic}, we have that $\| \beta \cdot \nabla u \|_{H^{l-1}(\Omega)} \leq \| \beta \|_{H^s(\Omega)}  \|u\|_{H^l(\Omega)}$ for $s > \max \{ l -1, \frac{d}{2}\}$. We can use this fact together with the bounds in \Eq{orthapprox} to bound the term $|I|$. Further, term $|IV|$ can easily be bounded as above and $II$ also vanishes. Finally, the term including $\|\beta\|_{W^{1,\infty}(\Omega)}$ does not appear when bounding $|III|$ (see Lemma \ref{lem-kappastab}), thus avoiding the exponential term in the final bound.
%The proof is similar to the one for Theorem \ref{th:conv}. Using \cite[Th. $1.4.4.2$]{grisvard2011elliptic}, one can affirm that if $\beta\in H^l(\Omega)^d$ for almost all $t\in(0,T)$, then $\beta\cdot v\in H^s(\Omega)$ for any $v\in H^s(\Omega)^d$, with $s\leq l$. Thus, using the optimal interpolant properties of the projector $\kappa_h(\cdot)$ for regular functions, the bounds for $|I|$ and $|IV|$ remain the same. Moreover  one can omit the term including $\|\beta\|_{W^{1,\infty}(\Omega)}$ when bounding $|III|$ (see Lemma \ref{lem-kappastab}), thus avoiding the exponential term in the final bound.
\end{proof}
\begin{remark}
Let us note that the following discussion can straightforwardly be generalized to CDR problems. However, diffusion and reaction terms introduce additional stability, namely $H^1(\Omega)$ and $L^2(\Omega)$ control, that is lost in the singular limit of pure convection. Most numerical analyses of convection FE stabilization techniques are carried out for CDR problems and many of them wrongly use the aforementioned control. As a result, bounds are not uniform with respect to physical parameters and blow-up in the interesting singular limit. A notable exception is the work in \cite{guermond_stabilization_1999}.
\end{remark}

@@

The next theorem states the strong DMP property for the proposed method.
\begin{theorem}
Let $\mathcal{T}_h$ be a strictly acute mesh. For $K\in \mathcal{T}_h$ let $c_{\rm gjv}$ be such that 
\begin{align}\label{eq-cgjv1}
c_{\rm gjv} \geq \frac{1}{(d+1) \sigma_K \sin \alpha_K}.
\end{align}
Then, the bilinear form
\begin{align}\label{eq-bfgjv}
a_h(u_h,\phi_h) = (\nabla \cdot ( \beta u_h), \phi_h) + (\varepsilon(u_h) \nabla u_h, \nabla \phi_h), 
\end{align}
with $\varepsilon(u_h)$ defined as in \Eq{gjvisc0}, satisfies  the strong DMP Definition \ref{strongDMP}  for any $q>0$.
\end{theorem}
\begin{proof}
Assume $u_h$ reaches a minimum on $x_i\in\Omega$. Then, testing \Eq{bfgjv} with $\varphi_h^i$ yields
\begin{align*}
 a_h(u_h,\varphi_h^i) = \sum\limits_{K\in\Omega_i} (\nabla \cdot  (\beta u_h), \varphi_h^i)_K + 
 (\varepsilon(u_h)|_K \nabla u_h, \nabla \varphi_h^i)_K.
\end{align*}
The convective term in each element $K$ can be bounded by
\begin{align*}
\int_K \nabla \cdot (\beta  u_h) \varphi_h^i {\rm d}\Omega \leq \int_K |\beta| |\nabla u_h| \varphi_h^i {\rm d}\Omega \leq \|\beta\|_{L^\infty(K)} |\nabla u_h| \frac{{\rm meas}(K)}{d+1}.
\end{align*}
On the other side, using Lemmata \ref{lem-extrema} and \ref{lem-stracute}, we can bound the artificial viscosity term by
\begin{align*}
\int_K \varepsilon(u_h) \nabla u_h, \nabla \varphi^i_h {\rm d}\Omega &  \leq \int_K c_{\rm gjv}|_K h_K \|\beta\|_{L^\infty(K)} |\nabla u_h| |\nabla \varphi_h^i| \cos \omega_{K,i}{\rm d}\Omega\\
&  \leq - c_{\rm gjv}|_K \|\beta\|_{L^\infty(K)} |\nabla u_h| \sigma_K \sin \alpha_K  {\rm meas}(K) \\
& \leq - \|\beta\|_{L^\infty(K)} |\nabla u_h| \frac{{\rm meas}(K)}{d+1}.
\end{align*}
Thus $a_h(u_h,\varphi_h^i) \leq 0$ if $u_h$ has a minimum on $x_i$. Similarly, one can prove that $a_h(u_h,\varphi_h^a) \geq 0$ if $u_h$ has a maximum on $x_i$, from what the DMP property follows.
\end{proof}

@@

We propose the following linear and nonlinear stabilization terms.\\

{\bf Linear stabilization:} We consider two different schemes, the wNPS method proposed in this work and the classical SUPG method. 
\setlength{\leftmargini}{0pt}
\begin{itemize}
\item  wNPS: We have two alternative versions of the symmetric stabilization term, namely 
\begin{align*}
  s_h(u_h,\phi_h) = ( \delta \beta \cdot \kappa_h^{\perp}(\nabla u_h), \beta \cdot \kappa_h^{\perp}(\nabla \phi_h)) \quad \hbox{or} \quad 
s_h(u_h,\phi_h) = ( \delta \kappa_h^{\perp}(\nabla\cdot (\beta u_h)),  \kappa_h^{\perp}(\nabla\cdot (\beta \phi_h)), 
\end{align*}
where $\kappa_h$ is the Scott-Zhang projector in \Eq{dualfunct}-\Eq{projSZ}, the node-to-element mapping $\varsigma$ is arbitrary and 
\begin{align*}%\label{eq-tildeltaSZ}
\delta|_K = \frac{c_\delta h_K}{\|\beta\|_{L^\infty(K)}}\left(1-\max_{a \in \mathcal{S}_h(K)}\left(\frac{ \jump{\nabla u_h}_a }{2\mean{|\nabla u_h|}_a}\right)^q\right).
\end{align*}
\item SUPG: The SUPG stabilization term reads as
\begin{align*}%\label{eq-supg}
s_h(u_h,\phi_h) = \sum_{K \in \mathcal{T}_h} c_{\delta} {h_K}{\| \beta \|_{L^\infty(K)}^{-1}}( \partial_t u_h + \nabla \cdot (\beta u_h), \nabla \cdot (\beta  \phi_h)), \nonumber 
\end{align*}
assuming that $\| \beta \|_{L^\infty(K)}>0$. If not, the contribution of the term corresponding to $K$ is $0$. 
\end{itemize}
In both cases, we take $c_\delta = 1/2$.

>>>>

In this chapter we introdue a linear/nonlinear stabilized FE formulations to approximate hyperbolic problems (and by extension singular limits of CDR systems). The outcomes of this research are:
\begin{itemize}
\item  We extend the NPS technique proposed in \cite{badia_stabilized_2012} for pressure stabilization to convection stabilization. We carry out the stability and convergence analysis, getting full control on the convection term (times a stabilization parameter).\footnote{This is an improvement of our analysis with respect to the one in \cite{rebollo_high_2013} for a similar formulation, which only provides partial control over convection, i.e., the component orthogonal to the FE space with respect to the aforementioned projector. However, the analysis in \cite{rebollo_high_2013} is not restricted to quasi-uniform meshes.}
\item Next, we show how to weight this linear stabilization in such a way that it  does not affect the potential  monotonicity of the underlying method. The use of the Scott-Zhang projector in the NPS stabilization turns out to be essential to design a linear stabilization that allows one to preserve DMP properties. 
\item 
Then we present some nonlinear stabilization, i.e., shock-capturing, methods with some  monotonicity properties. In particular, we design a method that enjoys a DMP for time-dependent multidimensional linear transport problems. 
%\item One of those methods is defined for the 1$D$ Burgers' equation and it is proved in  \cite{burman_nonlinear_2007} that it is not only monotonic but also entropy stable; thus an alternative blending between this nonlinear stabilization and the Scott-Zhang term is proposed in order to ensure that the combination mantains entropy stability.  
\item   We present a detailed numerical experimentation, where we show the excellent performance of the proposed algorithms in terms of elimination of oscillations, compared to some up-to-date shock-capturing schemes. 
%Using numerical experimentation, we show that one of the novel shock capturing techniques proposed in this work, %which can be considered a multidimensional extension of the one in \cite{burman_nonlinear_2007}, 
%produces results superior to any of the best up-to-date schemes, since it is provably monotonic. % (see \cite{john_spurious_2007,john_spurious_2008}). 
\end{itemize}

@@

Let us define $\bar{\delta} := c_{\delta} {h}{\| \beta \|_{L^\infty(\Omega)}^{-1}}$ if $\| \beta \|_{L^\infty(\Omega)}>0$ and $\bar{\delta} = 0$ otherwise. In the numerical analysis, we will assume that $\beta(t) \not = 0$ for any $t \in (0,T)$ for the sake of brevity, since the extension is obvious. Using the previous lemma we obtain the following stability result.
\begin{theorem}[Stability]
The solution $u_h$ of problem \Eq{SZstab} with the linear stabilization term $s_h(\cdot,\cdot)$ defined either by \Eq{stproj1} or \Eq{stproj2} and the projector $\kappa_h(\cdot)$ defined in \Eq{projSZ} 
%(either for the definitions \Eq{stproj1} or \Eq{stproj2} of the stabilization term) 
satisfies the bound
%$$
%\| u_h\|_{L^\infty(0,t^*;L^2(\Omega))} + \| \delta^\half \beta \cdot  \kappa_h
%^{\perp}(\nabla u_h)\|_{L^2(0,t^*;L^2(\Omega))} + \| |\beta \cdot n|^\half u_h\|_{L^2(0,t^*;L^2(\Gamma_{\rm out}))} \lesssim \|u_0\| + \|f\|_{L^\infty(0,t^*;L^2(\Omega))},
%$$
\begin{align*}
\| u_h\|_{L^\infty(0,t^*;L^2(\Omega))} &+ \|s_h(u_h,u_h)\|_{L^2(0,t^*)} + \| |\beta \cdot n|^\half u_h\|_{L^2( \Gamma_{\rm out} \times (0,t^*))} \\
 & \lesssim \|u_0\| + \|f\|_{L^1(0,t^*;L^2(\Omega))}
\end{align*}

for any $t^* \in (0,T)$. Further, it satisfies the weak inf-sup condition
\begin{align}\label{eq-dinfsup}
%\| \bar{\delta}^\half \beta \cdot \nabla u_h \| \lesssim  \| \bar\delta^\half\beta \cdot \kappa_h^{\perp}( \nabla u_h)\|  +
%\bar\delta^\half \|\beta\|_{W^{1,\infty}(\Omega)}  \|u_h\| + \sup_{\phi_h \in V_{h,0}} \frac{(\bar\delta^\half \nabla \cdot (\beta u_h),\phi_h)}{\|\phi_h\|}.
\| \bar{\delta}^\half \beta \cdot \nabla u_h \| \lesssim   s_h\left(u_h,u_h\right)  +
\gamma \bar\delta^\half \|\beta\|_{W^{1,\infty}(\Omega)}  \|u_h\| + \sup_{\phi_h \in V^k_{h,0}} \frac{(\bar\delta^\half \nabla \cdot (\beta u_h),\phi_h)}{\|\phi_h\|},
\end{align}
where $\gamma = 1$ for the stabilization term \Eq{stproj1} and $\gamma = 0$ for \Eq{stproj2}.
\end{theorem}

@@

Finally, we prove error estimates for this algorithm. We remark that linear projection stabilization methods are weakly consistent, i.e., the consistency error does not spoil the overall convergence rates, as soon as the projector $\kappa_h$ in \Eq{projSZ} has optimal approximation properties, i.e., for any $v\in W^{l,p}(\Omega)$ and $0\leq s \leq l \leq k+1$, it holds:
\begin{align}\label{eq-orthapprox}
\|\kappa_h^\perp(v)\|_{W^{s,p}(K)} \lesssim h^{l-s} \|v\|_{W^{l,p}(S_K)}, \qquad 
\|\kappa_h^\perp(v)\|_{W^{s,p}(\Omega)} \lesssim h^{l-s} \|v\|_{W^{l,p}(\Omega)},
\end{align}
where $S_K$ is a domain made of the elements neighboring $K$ (see \cite{brenner_mathematical_2010}).  We consider first the analysis for the  symmetric stabilization \Eq{stproj1}.
\begin{theorem}[Convergence]\label{th:conv}
Let $u_h \in V_h^k$ be the solution of \Eq{SZstab} with the linear stabilization term $s_h(\cdot,\cdot)$ defined in  \Eq{stproj1}  and the projector $\kappa_h(\cdot)$ defined in \Eq{projSZ}. Let us assume that the solution $u$ of \Eq{probcont} belongs to $L^\infty(0,T;H^l(\Omega))$ for $l \leq k+1$, and $\beta\in L^\infty(0,T;W^{1,\infty}(\Omega))$. The following error estimate holds for any $t^* \in (0,T)$:
\begin{align*}
& \|(u_h-u)(t^*)\| + \| \delta^\frac{1}{2} \bb \cdot \szpp \nabla  (u_h-u) \|_{L^2(\Qq)}   \\
%& \|(u_h-u)(t^*)\| + \|s_h(u_h-u,u_h-u)\|_{L^2(0,t^*)}   \\
%& \qquad \lesssim   h^{l} \|u(t^*)\|_{H^l(\Omega)}  +  h^{l-\half}\|\bb\|_{L^{\infty}(\Omega)}^\half \|u\|_{L^2(0,t^*;H^l(\Omega))} \left( 1 +  \exp\left( h t^* \|\bb\|_{W^{1,\infty}(Q)}^2\right)\right),
& \quad \lesssim 
  h^{l} \|u(t^*)\|_{H^l(\Omega)}  +  h^{l-\half}\|\bb\|_{L^{\infty}(\Qq)}^\half \|u\|_{L^2(0,t^*;H^l(\Omega))} \left( 1 + e^{t^* {\bar \delta } \|\bb  \|^2_{L^\infty(0,t^*;W^{1,\infty}(\Omega))}}
% \exp\left( t^* \left\|{\bar \delta {\|\bb\|_{W^{1,\infty}(\Omega)}^2}}\right\|_{L^\infty(0,t^*)}\right)
\right). 
\end{align*}
\end{theorem}

@@

\begin{theorem}[Convergence]\label{th:conv2}
Let $u_h \in V_h^k$ be the solution of \Eq{SZstab} with the linear stabilization term $s_h(\cdot,\cdot)$ defined in  \Eq{stproj2} and the projector $\kappa_h(\cdot)$ defined in \Eq{projSZ}. Let us assume that the solution $u$ of \Eq{probcont} belongs to $L^\infty(0,T;H^l(\Omega))$ for $l \leq k+1$, and $\beta\in L^\infty(0,T;{H}^s(\Omega))$ for $s>\max \{ l -1, \frac{d}{2}\}$. Then, the following error estimate holds for any $t^* \in (0,T)$:
\begin{align*}
 &\|(u_h-u)(t^*)\| + \| \delta^\frac{1}{2}  \szpp (\bb \cdot\nabla  (u_h-u)) \|_{L^2(\Qq)}   \\
&\quad \lesssim    h^{l} \|u(t^*)\|_{H^l(\Omega)}  +  h^{l-\half} \|\bb\|_{L^{\infty}(\Qq)}^\half \|u\|_{L^2(0,t^*;H^l(\Omega))}
+ h^{l-\half}  \| C_\beta \|u\|_{H^l(\Omega)} \|_{L^2(0,t^*)},
%+ h^{l-\half} \left \| \frac{\|\bb\|_{H^s(\Omega)} }{  \|\bb\|^\half_{L^\infty(\Omega)}} \|u\|_{H^l(\Omega)} \right \|_{L^2(0,t^*)}.
%, %\qquad \hbox{for any $t^* \in (0,T)$.}
\end{align*}
where $C_\beta=\min_{K \in \mathcal{T}_h} \|\beta\|_{H^{l-1}(S_K)}\|\beta\|^{-\half}_{L^\infty(K)}$.
\end{theorem}
\begin{proof}
The proof is similar to the one for Theorem \ref{th:conv}. Due to \cite[Th. $1.4.4.2$]{grisvard2011elliptic}, we have that $\| \beta \cdot \nabla u \|_{H^{l-1}(\Omega)} \leq \| \beta \|_{H^s(\Omega)}  \|u\|_{H^l(\Omega)}$ for $s > \max \{ l -1, \frac{d}{2}\}$. We can use this fact together with the bounds in \Eq{orthapprox} to bound the term $|I|$. Further, term $|IV|$ can easily be bounded as above and $II$ also vanishes. Finally, the term including $\|\beta\|_{W^{1,\infty}(\Omega)}$ does not appear when bounding $|III|$ (see Lemma \ref{lem-kappastab}), thus avoiding the exponential term in the final bound.
%The proof is similar to the one for Theorem \ref{th:conv}. Using \cite[Th. $1.4.4.2$]{grisvard2011elliptic}, one can affirm that if $\beta\in H^l(\Omega)^d$ for almost all $t\in(0,T)$, then $\beta\cdot v\in H^s(\Omega)$ for any $v\in H^s(\Omega)^d$, with $s\leq l$. Thus, using the optimal interpolant properties of the projector $\kappa_h(\cdot)$ for regular functions, the bounds for $|I|$ and $|IV|$ remain the same. Moreover  one can omit the term including $\|\beta\|_{W^{1,\infty}(\Omega)}$ when bounding $|III|$ (see Lemma \ref{lem-kappastab}), thus avoiding the exponential term in the final bound.
\end{proof}
\begin{remark}
Let us note that the following discussion can straightforwardly be generalized to CDR problems. However, diffusion and reaction terms introduce additional stability, namely $H^1(\Omega)$ and $L^2(\Omega)$ control, that is lost in the singular limit of pure convection. Most numerical analyses of convection FE stabilization techniques are carried out for CDR problems and many of them wrongly use the aforementioned control. As a result, bounds are not uniform with respect to physical parameters and blow-up in the interesting singular limit. A notable exception is the work in \cite{guermond_stabilization_1999}.
\end{remark}

@@

The next theorem states the strong DMP property for the proposed method.
\begin{theorem}
Let $\mathcal{T}_h$ be a strictly acute mesh. For $K\in \mathcal{T}_h$ let $c_{\rm gjv}$ be such that 
\begin{align}\label{eq-cgjv1}
c_{\rm gjv} \geq \frac{1}{(d+1) \sigma_K \sin \alpha_K}.
\end{align}
Then, the bilinear form
\begin{align}\label{eq-bfgjv}
a_h(u_h,\phi_h) = (\nabla \cdot ( \beta u_h), \phi_h) + (\varepsilon(u_h) \nabla u_h, \nabla \phi_h), 
\end{align}
with $\varepsilon(u_h)$ defined as in \Eq{gjvisc0}, satisfies  the strong DMP Definition \ref{strongDMP}  for any $q>0$.
\end{theorem}
\begin{proof}
Assume $u_h$ reaches a minimum on $x_i\in\Omega$. Then, testing \Eq{bfgjv} with $\varphi_h^i$ yields
\begin{align*}
 a_h(u_h,\varphi_h^i) = \sum\limits_{K\in\Omega_i} (\nabla \cdot  (\beta u_h), \varphi_h^i)_K + 
 (\varepsilon(u_h)|_K \nabla u_h, \nabla \varphi_h^i)_K.
\end{align*}
The convective term in each element $K$ can be bounded by
\begin{align*}
\int_K \nabla \cdot (\beta  u_h) \varphi_h^i {\rm d}\Omega \leq \int_K |\beta| |\nabla u_h| \varphi_h^i {\rm d}\Omega \leq \|\beta\|_{L^\infty(K)} |\nabla u_h| \frac{{\rm meas}(K)}{d+1}.
\end{align*}
On the other side, using Lemmata \ref{lem-extrema} and \ref{lem-stracute}, we can bound the artificial viscosity term by
\begin{align*}
\int_K \varepsilon(u_h) \nabla u_h, \nabla \varphi^i_h {\rm d}\Omega &  \leq \int_K c_{\rm gjv}|_K h_K \|\beta\|_{L^\infty(K)} |\nabla u_h| |\nabla \varphi_h^i| \cos \omega_{K,i}{\rm d}\Omega\\
&  \leq - c_{\rm gjv}|_K \|\beta\|_{L^\infty(K)} |\nabla u_h| \sigma_K \sin \alpha_K  {\rm meas}(K) \\
& \leq - \|\beta\|_{L^\infty(K)} |\nabla u_h| \frac{{\rm meas}(K)}{d+1}.
\end{align*}

Thus $a_h(u_h,\varphi_h^i) \leq 0$ if $u_h$ has a minimum on $x_i$. Similarly, one can prove that $a_h(u_h,\varphi_h^a) \geq 0$ if $u_h$ has a maximum on $x_i$, from what the DMP property follows.
\end{proof}

@@

We propose the following linear and nonlinear stabilization terms.

{\bf Linear stabilization:} We consider two different schemes, the wNPS method proposed in this work and the classical SUPG method. \\
%\setlength{\leftmargini}{0pt}
\begin{algorithmic}[1]
\State wNPS: We have two alternative versions of the symmetric stabilization term, namely
\begin{displaymath}
s_h(u_h,\phi_h) = ( \delta \beta \cdot \kappa_h^{\perp}(\nabla u_h), \beta \cdot \kappa_h^{\perp}(\nabla \phi_h))
\end{displaymath} 
  or 
\begin{align*}
s_h(u_h,\phi_h) = & ( \delta \kappa_h^{\perp}(\nabla\cdot (\beta u_h)),  \kappa_h^{\perp}(\nabla\cdot (\beta \phi_h)), 
\end{align*}
where $\kappa_h$ is the Scott-Zhang projector in \Eq{dualfunct}-\Eq{projSZ}, the node-to-element mapping $\varsigma$ is arbitrary and 
\begin{align*}%\label{eq-tildeltaSZ}
\delta|_K = \frac{c_\delta h_K}{\|\beta\|_{L^\infty(K)}}\left(1-\max_{a \in \mathcal{S}_h(K)}\left(\frac{ \jump{\nabla u_h}_a }{2\mean{|\nabla u_h|}_a}\right)^q\right).
\end{align*}
\State SUPG: The SUPG stabilization term reads as
\begin{align*}%\label{eq-supg}
s_h(u_h,\phi_h) = \sum_{K \in \mathcal{T}_h} c_{\delta} {h_K}{\| \beta \|_{L^\infty(K)}^{-1}}( \partial_t u_h + \nabla \cdot (\beta u_h), \nabla \cdot (\beta  \phi_h)). \nonumber 
\end{align*}
If $\| \beta \|_{L^\infty(K)}=0$, the contribution of the term corresponding to the element $K$ is $0$. 
\end{algorithmic}

In both cases, we take $c_\delta = 1/2$.\\

\textbf{Nonlinear stabilization:} We propose two different GJV shock-capturing schemes and we test them against the RV and EV schemes.
%\setlength{\leftmargini}{0pt}
\begin{algorithmic}[1]
\State nGJV: In the nodal GJV scheme the artificial diffusion is defined at $K \in \mathcal{T}_h$ as
\begin{align*}%\label{eq-gjvisc0}
\varepsilon(u_h)|_K = c_{\rm gjv}|_K h_K \|\beta\|_{L^\infty(K)} \max_{a \in \setnodes(K)}\left(\frac{ \jump{\nabla u_h}_a }{2\mean{|\nabla u_h|}_a}\right)^q,
\end{align*}
where $c_{\rm gjv} = \frac{1}{(d+1) \sigma_K \sin (\pi/6)}$. %In order to satisfy the DMP on acute meshes, we take $c_{\rm gjv} = \frac{1}{(d+1) \sigma_K \sin \alpha_K}$, with the definition of $\alpha_K$ in \Eq{gjvisc0}.
\State bGJV: In the boundary GJV scheme the artificial diffusion is defined at $K \in \mathcal{T}_h$ as
\begin{align*}%\label{eq-gjvisc}
\varepsilon(u_h)|_K = \tilde c_{\rm gjv} h \|\beta\|_{L^\infty(K)} \max_{e \in \partial K}\left[\frac{\int_e |\nabla u_h \cdot n|{\rm d} \sigma}{\int_e |\nabla u_h| {\rm d} \sigma}\left(\frac{\int_e  | \jump{\nabla u_h}|{\rm d} \sigma }{ 2 \int_e \mean{|\nabla u_h \cdot n|} {\rm d} \sigma}\right)^q\right],
\end{align*}
where $\tilde c_{\rm gjv} = 1/2$.
\State EV: The scheme is defined in \Eq{ev} with $\eta(u_h) = (u_h-0.5)^2$, $\psi(u_h) = \beta(u_h-0.5)^2$, $c_{\rm ent} = 0.1$ and $c_{\rm max}=0.15$. 
\State RV: In the RV  scheme the artificial diffusion is defined at $K \in \mathcal{T}_h$ as $\varepsilon(u_h)|_K = \nu_K(u_h) |\mathcal{R}(u_h)|^q$ where $\nu_K$ is defined in \Eq{isosc} with $l_K^{\rm iso}=0.6$ and $\tau_K^{\rm iso}=0$.
\end{algorithmic}
\caption{Combination of linear stabilization and shock-capturing techniques\label{alg-wNPS-GJV}}
\end{algorithm}
